The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-04 src/ms.tex
missing "is"

Major versions of the core package --- that is, versions that add and/or modify
functionality --- are released approximately every six months, and are then
maintained with releases that fix issues until the next major version is
released. However, every two years a major release is designated as a long-term
support (LTS) release, which continues to be maintained for up to two years
\citep{ape2}. The motivation for LTS releases is to provide longer-term stable
versions of \astropypkg that users who require a high level of stability can
make use of if they do not always need the latest features (this includes but
not limited to telescope operations and data reduction pipelines). The v5.0
release of the core package, replacing v4.0, was designated as LTS at the end of 2021;
it will be maintained until the end of 2023.

>>>>

Major versions of the core package --- that is, versions that add and/or modify
functionality --- are released approximately every six months, and are then
maintained with releases that fix issues until the next major version is
released. However, every two years a major release is designated as a long-term
support (LTS) release, which continues to be maintained for up to two years
\citep{ape2}. The motivation for LTS releases is to provide longer-term stable
versions of \astropypkg that users who require a high level of stability can
make use of if they do not always need the latest features (this includes but
is not limited to telescope operations and data reduction pipelines). The v5.0
release of the core package, replacing v4.0, was designated as LTS at the end of 2021;
it will be maintained until the end of 2023.
